### 2023-10-29 conclusions/conclusion.tex
Reading to make sure nothing is missing
More corrections

More complex input sequences produce even more inaccuracies. Indeed, when working with sequence 15 (\cref{graph:io15Celegans}), the inaccuracies spiral up and gives out a barely usable prediction. The curve generated does not fit its digital counterpart anymore.

The results obtained demonstrate that the \ac{LSTM} circuit block can be run with low error when dealing with simple inputs. The circuit is assumed to be ready for a full simulation, meaning also training with the analog circuit.

>>>>

More complex input sequences produce even more inaccuracies. Indeed, when working with sequence 15 (\cref{graph:io15Celegans}), the inaccuracies explode and gives out a barely usable prediction. The curve generated does not fit its digital counterpart anymore.

The results obtained demonstrate that the \ac{LSTM} circuit block can be run with low error when dealing with simple inputs. The circuit is ready for a full simulation, meaning also simulating training with the analog circuit.
